``Colloidal cold rain'' as a novel route to crystallization via viscoelastic phase separation

### 2015-10-18 science/SOM2.tex
correct tauB and formulation of supplementary movies description

\noindent
{\bf Experimental.}
We use \textsc{pmma} (poly(methyl methacrylate)) colloids sterically stabilized with methacryloxypropyl terminated \textsc{pdms}(poly(dimethyl siloxane)) and fluorescently labelled with rhodamine isothiocyanate chemically bonded to the \textsc{pmma}. 
The average colloid diameter is 2.2 $\mu$m, measured via the diffusion constant in dilute conditions without polymer. The Brownian time is $\tau_B \approx 2.3$ s. 
We assess that the size distribution of our particle is Gaussian with a polydispersity below 5\% via direct confocal measurements~\cite{Leocmach2013}.
This small polydispersity allows crystallization.
We disperse the particles in refractive index and density matching mixture of cis-decalin (Tokyo Kasei) and bromocyclohexane (Sigma-Aldrich). 
The precision of density matching is $\sim 10^{-4}$ mg/ml, for which the gravity effect on our gelation processes is negligible up to 12 hours.

@@

>>>>

\noindent
{\bf Experiments}

We use \textsc{pmma} (poly(methyl methacrylate)) colloids sterically stabilized with methacryloxypropyl terminated \textsc{pdms}(poly(dimethyl siloxane)) and fluorescently labelled with rhodamine isothiocyanate chemically bonded to the \textsc{pmma}. 
The average colloid diameter is 2.2 $\mu$m, measured via the diffusion constant in dilute conditions without polymer. The Brownian time is $\tau_B \approx 2.3$ s. 
We assess that the size distribution of our particle is Gaussian with a polydispersity below 5\% via direct confocal measurements~\cite{Leocmach2013}.
This small polydispersity allows crystallization.
We disperse the particles in refractive index and density matching mixture of cis-decalin (Tokyo Kasei) and bromocyclohexane (Sigma-Aldrich). 
The precision of density matching is $\sim 10^{-4}$ mg/ml, for which the gravity effect on our gelation processes is negligible up to 12 hours.

@@

\noindent
{\bf Supplementary Movies}

\emph{Supplementary Movie 1}. This movie shows the early stage of gelation process of $\phi\approx 0.30$ and $c_p=0.38$ mg/g, from the original confocal images at the same z-position as Fig.~3A. Total duration is 1160 s (~530~$\tau$). We quickly started scanning the sample after exchanging the salt-reservoir with the solvent including salt. At the beginning, salt had not reached the scanning volume and colloids were dispersed by electrostatic repulsion. At 0:02 in the movie, salt diffused into the scanning volume and screened the surface charges of colloids. Then, colloids immediately initiated phase separation by short-ranged attractions.

\emph{Supplementary Movie 2}.
This movie shows the late stage after Supplemental Movie 1 with scanning duration of 27000~s (~12300$\tau$).
